\documentclass{res}
\usepackage{hyperref}
\usepackage{tabularx}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[C]{\thepage}

\begin{document}

\name{\LARGE{Josh Ghiloni}}
\address{(303) 590-5427}
\address{ghiloni@gmail.com}

\begin{resume}

\section{OBJECTIVE}\vspace{10pt}
To change the world, of course. I have nearly three decades of experience in the
technology space and I am obsessed with using that acquired experience and skill
to make people's lived experiences more rewarding and comfortable.

\section{SELECTED WORK EXPERIENCE}\vspace{10pt}

\employer{\textbf{Havrion, LLC}}
\title{\textbf{VP of Engineering / Chief Programmer}}
\dates{\textbf{August 2024 – November 2025}}
\location{}
\begin{position}
Havrion is a company in the digital signage space with a simple value proposition:
You've already spent a ton of money on your displays; you shouldn't need to spend
more on hardware to make it do what you want it to do.

When I began there, Havrion was tightly coupled to the Samsung ecosystem, with its
solution running on the Samsung commercial display System-on-a-chip (SOC). My charge
was to bring modern software practices to a firm that is largely based in the
hardware world. As part of that charge, I brought the Lean Product Management
ceremonies learned from my time at Pivotal, as well as modern concepts such as
continous delivery and observability.

I also strived to widen our total addressable market by freeing us from the tight
bonds with Samsung and moving us to a hardware-agnostic solution. I was nearing
completion of the first iteration of that effort in November 2025, when a reorganization
from Havrion's parent company eliminated my position.
\end{position}

\employer{\textbf{Realtor.com}}
\title{\textbf{Principal Software Engineer}}
\dates{\textbf{March 2022 – January 2024}}
\location{}
\begin{position}
I was hired at RDC to be the technical lead for the SRE team. We were a small
team of primarily young engineers, and my goal was to impart my knowledge of SRE
practices obtained from direct experience and from teaching other teams how to
effectively implement the teachings in their own organizations.

After a reorganization in September 2022, our team became focused on quality for
the consumer-facing parts of the site. This entailed maintaining and improving
several internal testing tools, including k6 for performance testing, and
Sitespeed.io for core web vital testing. In addition, we provide reporting tools
for product quality, including Avalability reporting, defect burndowns, and SEO
scores. We do this primarily by maintaining tools that extract data from various
sources of truth and capturing summarized reports in a data warehouse.

We worked to migrate existing tools from a primarily AWS ECS-based deployment
strategy to EKS-based deployments, and I enjoyed mentoring my team on basic
k8s topics like RBAC and scheduling, and more advanced topics like custom resource
definitions and operators.

In addition to these primary responsibilities, as the technical lead and senior member
of the team, I acted as a liaison between management and the team. This involved parsing
often ambiguous requirements from management and converting them into actionable steps
for these young, talented engineers. I also enjoyed the opportunity to unofficially
mentor each of them, both individually and as a group. During that time, I distilled
complex technical requirements with them, taught them new skills, and acted as a
guide as they navigate life in a corporate environment, often for the first time in
their careers.
\end{position}

\employer{\textbf{Pivotal Software / VMware}}
\title{\textbf{Staff Solutions Architect}}
\dates{\textbf{July 2017 – February 2022}}
\location{}
\begin{position}
Along with my world-class team of client-facing Solutions Architects as
part of VMware Tanzu Labs (formerly Pivotal Labs), I helped my clients transform the way they build
and run software platforms. My job entailed shepherding a team of client
platform engineers, product managers, and designers through their journey
in deploying and effectively using the VMware Tanzu suite and delivering value
to their customers, which are usually in-house development teams. I focused on building
Site Reliability Engineering compentencies, as well fostering automation-first,
security-first architectures.

From May 2020 until my departure in early 2022, I led the delivery of a small in-house SRE team as we piloted
a new managed service offering for our customers. In this capacity, I was
able to take the SRE knowledge that we impart to our customer SRE teams,
implement it myself, and work to continously improve upon that knowledge
base. I led incident post-mortems with our customers, as well as kept them
up to date on the health and status of their platform.
\end{position}

\employer{\textbf{ECSTeam, Inc., now part of CGI}}
\title{\textbf{Principal Consultant}}
\dates{\textbf{November 2012 - July 2017}}
\location{}
\begin{position}
As a boutique IT consultancy in Denver, CO, my time with ECSTeam first
started as an infrastructure architect for Connect for Health Colorado,
the ACA Exchange for the state of Colorado, based on Oracle's middleware suite.
Colorado's Exchange holds the esteemed honor of being the only exchange,
state or federal, that did not experience an outage on October 1, 2013,
the day the exchanges were statutorily required to go live.

After that, I worked with a company that provides global imaging for both
military and commercial customers. Using my polyglot skills, I was tasked
with, and ultimately successful at, creating a unified system-to-system
authentication and authorization system. This system had a similar, yet
still idiomatic to each language, developer experience across their Java,
Python, and Ruby applications.

Later, I became part of a small practice within the company focused on
emerging cloud technologies. As we became a Pivotal Ready Partner, I
participated in Pivotal Cloud Foundry engagements beginning in 2016. In that
context, I was involved with many of the same type of engagements that I
lead throughout my tenure at Pivotal.
\end{position}

\centering{\textbf{\textsl{Further Employment History Available Upon Request}}}

\pagebreak

\section{PROGRAMMING LANGUAGES}\vspace{10pt}

\begin{tabularx}{\linewidth}{XXX}
\textbf{Language} & \textbf{Skill Level} & \textbf{Years Used} \\
Go & Expert & 2014 – Present \\
Typescript / Javascript & Expert & 2006 – Present \\
Java & Advanced & 2006 – 2019 \\
C\# / .NET & Advanced & 2002 – Present \\
Python & Intermediate & 2014 – Present \\
C / C++ & Intermediate & 1997 – 2010 \\
\end{tabularx}

\section{TECH STACKS}\vspace{10pt}
\raggedright

\textbf{Cloud Hyperscalers}: AWS, Azure, GCP, Linode, vSphere, Proxmox VE \\
\textbf{Container Runtimes}: Kubernetes, Docker / Docker Compose, Cloud Foundry \\
\textbf{Backend Frameworks}: Echo, Fiber, Spring Boot, Express, NestJS, Flask \\
\textbf{Frontend Frameworks}: React, jQuery, Wails, .NET Maui \\
\textbf{Databases}: PostgreSQL / PostGIS, MySQL, SQLite, MS SQL Server, Redis, DynamoDB, MongoDB \\
\textbf{CI/CD}: Github Actions, Concourse CI, CircleCI, ArgoCD \\
\textbf{Observability}: Prometheus, Loki, Grafana, InfluxDB \\

\section{CERTIFICATIONS}\vspace{10pt}
{\bf Certified Kubernetes Administrator} \\
Certification Number \texttt{CKA-2000-007976-0100} \\
Earned May 2020, Expired May 2023

{\bf Certified Kubernetes Application Developer} \\
Certification Number \texttt{CKAD-2000-003980-0100} \\
Earned May 2020, Expired May 2023

{\bf Certified Kubernetes Security Specialist} \\
Certification Number \texttt{LF-2qktgivcfa} \\
Earned July 2021, Expired July 2023

\section{SELECTED SPEAKING}\vspace{10pt}
{\bf April 2022} \\
Internal realtor.com technical conference - Techcelerate \\
On the Benefits of Building and Maintaining a Balanced Product Team

{\bf April 2019} \\
Cloud Foundry Summit North America \\
\href{https://youtu.be/ydswsuidHn4}{Cracks in the Foundation - Lessons Learned from Operating Platforms at Scale}

\vspace{20pt}
\centering{\textbf{\textsl{\large{Character and Experience References Available Upon Request}}}}

\end{resume}
\end{document}
